%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {Software Engineer \& Open Source community leader} % Job title
    {OpenIM(https://github.com/openimsdk)} % Organization
    {ShenZhen, China} % Location
    {Apr. 2023 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as an evangelist for OpenIM, leading the establishment and development plan of the entire community.}
        \item {Independently established, operated, and maintained the Slack platform for the community, integrating automation. (Slack invite link: \href{https://join.slack.com/t/openimsdk/shared_invite/zt-22720d66b-o_FvKxMTGXtcnnnHiMqe9Q}{OpenIMSDK Slack})}
        \item {Proposed, designed, planned, and managed the OpenKF project. Responsible for project planning, maintenance, and coordinating project members. Also participated in coding and code reviews. (\href{https://github.com/OpenIMSDK/OpenKF}{OpenKF GitHub Repository})}
        \item {Regularly undertook large-scale feature design and refactoring tasks for the OpenIM Server. Became a core member of the top-tier OpenIM Server open-source project (with stars > 12k). Led in terms of issue and PR contributions. (\href{https://github.com/OpenIMSDK/Open-IM-Server}{OpenIM Server GitHub Repository})}
        \item {Achieved a high-quality deployment experience for OpenIM, including designing and planning script initiation projects, support for Linux systems, Linux daemon processes, and one-click docker compose deployments.}
        \item {Optimized Docker networking, supported multi-architecture compilation of OpenIM images, multi-registry support, and offline deployment capabilities.}
        \item {Greatly expanded script projects, incorporated automated processes, and designed a comprehensive Makefile system, ensuring a robust foundation for OpenIM.}
        \item {Formulated and implemented OpenIM's cluster deployment strategy, including support for Kubernetes, microservice image segmentation, construction, and automation.}
        \item {Enhanced the overall engineering capabilities of OpenIM Server, encompassing logging, tags, commits, and a robust CI/CD automated deployment and testing system.}
        \item {Executed functional designs for OpenIM Server, including the core command-line tool design of Imctl, client and server version designs, and module deletion designs.}
      \end{cvitems}
    }



%---------------------------------------------------------
\end{cventries}
